Comparative Analysis of the wav2vec 2.0 Feature Extractor

### 2023-03-09 main.tex
add contributions text

\draft{
Highlight contributions of this paper.
}

@@

\subsubsection{Supervised Convolutional Features}
As an alternative comparable neural feature extraction method, we use \gls{SC} features \cite{tuske2018:waveform, vieting2021waveform}.
Similarly, a convolutional filterbank with learnable parameters is applied to the waveform.
As in the case of Gammatones, a temporal integration is performed over each channel.
However, in this case multiple filters are used for temporal integration allowing for multi-resolutional processing.
Additionally, these filters are learned during training.
By default, we set the size of the first filterbank to 160, its strides to 10 and the number of channels to 150.
The second convolutional filter applies 5 temporal integration filters with a size of 40 and strides of 16 each.
Since the output of all 5 filters is stacked, we have a resulting feature dimension of 750.
The total receptive field of the \gls{SC} features is \ms{40}.

>>>>

In this work, we show new insights into the \wvtwo \fe.
Unlike previous work, we demonstrate that it can be used as a replacement for traditional feature extraction methods for a \gls{CTC} model similar to \gls{SC} features.
The results show that both are competitive on the LibriSpeech benchmark.
We analyze the learned filters and show the differences between the characteristics of both neural \fes.
Finally, we demonstrate that the learned bandpass filters of the \gls{SC} \fe encode the valuable information for the \gls{ASR} system while the remaining wideband filter information is largely ignored.

@@

\subsubsection{Supervised Convolutional Features}
As an alternative comparable neural feature extraction method, we use the \gls{SC} features from \cite{tuske2018:waveform, vieting2021waveform}.
Similarly, a convolutional filterbank with learnable parameters is applied to the waveform.
As in the case of Gammatones, a temporal integration is performed over each channel.
However, in this case multiple filters are used for temporal integration allowing for multi-resolutional processing.
Additionally, these filters are learned during training.
By default, we set the size of the first filterbank to 160, its strides to 10 and the number of channels to 150.
The second convolutional filter applies 5 temporal integration filters with a size of 40 and strides of 16 each.
Since the output of all 5 filters is stacked, we have a resulting feature dimension of 750.
The total receptive field of the \gls{SC} features is \ms{40}.
